\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-01 gwnnDraft02.tex
pull stuff

Shifting to the other part of our framework, our results leads to the question "are current experiments able to probe non power law signals?" For frequency ranges away from the peak of the total GW signals the quoted detection thresholds should hold: the signals fall off in a fashion identical to a power law. However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law. This points to the need for future work to better understand detection prospects for the next generation of GW detectors.

>>>>

Shifting to the other part of our framework, our results leads to the question ``are current experiments able to probe non power law signals?" For frequency ranges away from the peak of the total GW signals the quoted detection thresholds should hold: the signals fall off in a fashion identical to a power law. However, for areas around the peak frequency the answer is less clear; the PLI curves are built under the assumption of a power law. This points to the need for future work to better understand detection prospects for the next generation of GW detectors.
